Unimodular covers of 3-dimensional\\ parallelepipeds and Cayley sums

### 2023-09-26 ct-final/unimodular-covers-ctstyle.tex
ctstyle version

\documentclass{amsart}

\textheight=22.5cm
\topmargin=0.5cm

\usepackage{amssymb}
\usepackage{graphicx,color}
\usepackage{amsmath}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}
\usepackage{doi}
%\usepackage{pictex}

\usepackage{cleveref}
\Crefname{counterexample}{counterexample}{counterexamples}
\Crefname{counterexample}{Counterexample}{Counterexamples}
\Crefname{conjecture}{conjecture}{conjectures}
\Crefname{conjecture}{Conjecture}{Conjectures}

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{tkz-euclide}
\usetikzlibrary{intersections}
%\usetkzobj{all}

\newcommand{\limites}{}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{claim}[theorem]{Claim}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{example}[theorem]{Example}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{question}[theorem]{Question}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{remark}[theorem]{Remark}

% Macros in general

\newcommand{\F}{ \ensuremath{\mathbb{F}}}
\newcommand{\N}{ \ensuremath{\mathbb{N}}}
\newcommand{\Z}{ \ensuremath{\mathbb{Z}}}
\newcommand{\C}{ \ensuremath{\mathbb{C}}}
\newcommand{\R}{ \ensuremath{\mathbb{R}}}

\newcommand{\T}{ \ensuremath{\mathcal{T}}}

\newcommand{\bb}{{\mathbf{b}}}
\newcommand{\cc}{{\mathbf{c}}}
\newcommand{\ttt}{\mathbf{t}}
\newcommand{\GL}{{GL}_r (K)}

\renewcommand{\int}{\operatorname{int}}
\newcommand{\width}{\operatorname{width}}
\newcommand{\ind}{\operatorname{index}}
\newcommand{\Vol}{\operatorname{Vol}}
\newcommand{\area}{\operatorname{area}}
\newcommand{\length}{\operatorname{length}}

\renewcommand{\vec}[1]{\overrightarrow#1}
\newcommand{\vecline}[1]{\langle \vec #1 \rangle}

\newcommand{\cone}{\ensuremath{\mathrm{cone}}\hspace{1pt}}
\newcommand{\conv}{\ensuremath{\mathrm{conv}}\hspace{1pt}}
\newcommand{\cayley}{\operatorname{Cay}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\reg}{\operatorname{reg}}

\newcommand{\Image}{\ensuremath{\mathrm{Im}}\hspace{1pt}}

\usepackage[colorinlistoftodos]{todonotes}

\newcommand{\giulia}[1]{\todo[size=\tiny,color=blue!30]{#1 \\ \hfill --- G.}}
\newcommand{\Giulia}[1]{\todo[size=\tiny,inline,color=blue!30]{#1 \\ \hfill --- G.}}

\newcommand{\paco}[1]{\todo[size=\tiny,color=green!30]{#1 \\ \hfill --- P.}}
\newcommand{\Paco}[1]{\todo[size=\tiny,inline,color=green!30]{#1 \\ \hfill --- P.}}

\date{\today}

%\author[G.~Codenotti]{Giulia Codenotti}
%\author[F.~Santos]{Francisco Santos}

%\address[G.~Codenotti]
%{
%Institut f\"ur Mathematik, Freie Universit\"at Berlin, Germany
%}
%\email{codenotti@math.uni-frankfurt.de}

%\address[F.~Santos]
%{
%Department of Mathematics, Statistics and Computer Science, University of Cantabria, Spain
%}
%\email{francisco.santos@unican.es}

%\thanks{The authors were supported by the Einstein Foundation Berlin under grant EVF-2015-230. 
%Work of F. Santos is also supported by grants PID2019-106188GB-I00 funded by MCIN/AEI/10.13039/501100011033 and by FPU19/04163 of the Spanish Government and by project CLaPPo (21.SI03.64658) of Universidad de Cantabria and Banco Santander}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Unimodular covers of 3-dimensional parallelepipeds and Cayley sums}
\author{}

\begin{document}

@@

@@

\subsection*{Acknowledgements:} We  thank two anonymous referees for helpful comments on a previous version of this paper.

@@

\begin{thebibliography}{99}

\bibitem{BHHHJKM2019}
Matthias Beck, Christian Haase, Akihiro Higashitani, Johannes Hofscheier, Katharina Jochemko, Lukas Katth\"an, Mateusz Micha{\l}ek,
Smooth Centrally Symmetric Polytopes in Dimension 3 are IDP,
\emph{Ann.~Combin.}, 23 (2019), 255--262.
\doi{10.1007/s00026-019-00418-x}

\bibitem{BG}
Winfried Bruns and Joseph Gubeladze, Normality and covering properties of affine semigroups, \emph{J. Reine Angew. Math.} 510 (1999), 151--178. \doi{10.1515/crll.1999.044}

\bibitem{BGbook}
Winfried Bruns and Joseph Gubeladze, \emph{Polytopes, rings, and k-theory}, Monographs in Mathematics,
  Springer-Verlag, 2009, XIV, 461 p. 52 illus.

\bibitem{BGM}
  Winfried Bruns, Joseph Gubeladze, and Mateusz Micha{\l}ek. Quantum Jumps of Normal Polytopes. \emph{Discrete Comput. Geom.}, 56(1) (2016), 181--215. \doi{10.1007/s00454-016-9773-7}

\bibitem{CLS}
David A.~Cox, John B.~Little, and Hal K.~Schenck.
{\em {T}oric {V}arieties}.
AMS, Providence, 2011.

 \bibitem{DLRS2010}
J. A. De Loera, J. Rambau, F. Santos
\emph{Triangulations: Structures for Algorithms and Applications}, 539 pp.
Algorithms and Computation in Mathematics, Vol. 25, Springer-Verlag. 
ISBN: 978-3-642-12970-4

\bibitem{Fakhruddin}
Najmuddin Fakhruddin.
\newblock Multiplication maps of linear systems on smooth projective toric surfaces.
  Preprint, 
  \href{https://arxiv.org/abs/math/0208178}{arXiv:math/0208178}, August 2002.

%\bibitem{Grunbaum}
%{Branko Gr\"unbaum}.
%{\em {C}onvex {P}olytopes}.
%Wiley, London, 1967.

\bibitem{Gubeladze}
Joseph Gubeladze,
Normal polytopes and ellipsoids,
\emph{Elect. J. Combin.}, 28:4 (2021), P4.7.
\doi{10.37236/10338}

\bibitem{HaaseHof}
Christian Haase and Jan Hofmann, 
Convex-normal (Pairs of) Polytopes, 
\emph{Canad. Math. Bull.} 60:3 (2017), 510--521. \doi{10.4153/CMB-2016-057-0}

  \bibitem{HPPS-survey}
Christian Haase, Andreas Paffenholz, Lindsay C. Piechnik, Francisco Santos. Existence of unimodular triangulations - positive results. 
 \emph{Mem. Amer. Math. Soc.},  Vol.~270 1N.~321, American Math. Society, 2021. DOI: \doi{10.1090/memo/1321}
%ISBNs: 978-1-4704-4716-8 (print); 978-1-4704-6530-8 (online)

\bibitem{HNPS2008}
Christian Haase, Benjamin Nill, Andreas Paffenholz, and Francisco Santos, Lattice points in Minkowski sums, 
\emph{Electron.~J.~Combin.}, 15:1 (2008), Note 11, 5 pp. \doi{10.37236/886}

\bibitem{KantorSarkaria}
Jean-Michel Kantor and Karanbir~S.\ Sarkaria.
On primitive subdivisions of an elementary tetrahedron, 
\emph{Pacific J.~Math.} \textbf{211} (2003), no.~1,  123--155. \doi{10.2140/pjm.2003.211.123}

\bibitem{mfo2004}
Mini-workshop: Ehrhart Quasipolynomials: Algebra, Combinatorics, and Geometry, Oberwolfach Rep. 1 (2004), no. 3, 2071-2101, Abstracts from the mini-workshop held August 15-21, 2004, Organized by Jes\'us A.~De Loera and Christian Haase, Oberwolfach Reports. Vol. 1, no. 3. \doi{10.14760/OWR-2004-39}

\bibitem{mfo2007}
Mini-workshop: Projective normality of smooth toric varieties, Oberwolfach Rep. 4 (2007), no. 39/2007, Abstracts from the mini-workshop held August 12-18, 2007. Organized by Christian Haase, Takayuki Hibi and Diane MacLagan. \doi{10.14760/OWR-2007-39}

\bibitem{Oda1997}
Tadao Oda. Problems on Minkowski sums of convex lattice polytopes. 
Abstract submitted at the Oberwolfach Conference ''Combinatorial Convexity and Algebraic Geometry'' 26.10--01.11, 1997.
Available as arXiv preprint \href{https://arxiv.org/abs/0812.1418}{arXiv:0812.1418}, 2008.

\bibitem{Ogata}
Shoetsu Ogata.
\newblock {Multiplication maps of complete linear systems on projective toric surfaces.}
\newblock {\em Interdiscip. Inf. Sci.}, 12(2):93--107, 2006. \doi{10.4036/iis.2006.93}

\bibitem{Santos-hirsch}
Francisco Santos.
A counter-example to the Hirsch Conjecture.
\emph{Ann.~Math.~(2)}, 176 (July 2012), 383--412. 
\doi{10.4007/annals.2012.176.1.7}

\bibitem{SantosZiegler}
Francisco Santos and G{\"u}nter~M. Ziegler.
\newblock {Unimodular triangulations of dilated 3-polytopes}, 
\newblock {\em Trans. Moscow Math. Soc.} (2013), 293--311. \doi{10.1007/s00493-014-2959-9}

\bibitem{Tsuchiya}
Akiyoshi Tsuchiya.
Cayley sums and Minkowski sums of 2-convex-normal lattice polytopes.
Preprint,  \href{https://arxiv.org/abs/1804.10538}{arXiv:1804.10538}, April 2018.

\bibitem{White1964}
G.~K.~White.
Lattice tetrahedra.
\emph{Canadian J.~Math.} 16 (1964), 389--396. \doi{10.4153/CJM-1964-040-2}

\end{thebibliography}

>>>>

% SAMPLE ARTICLE FOR COMBINATORIAL THEORY
%
% CT papers *must* follow this sample file.
% Please, do not erase comments in the head of this sample file as
% they are used to process your file semi-automatically.

% COPYRIGHT NOTICE
% We use the CC BY licence. It allows others to freely distribute 
% your work while giving credit to you. In particular CC BY allows 
% remixing, tweaking and building upon your work.  
% See https://creativecommons.org/licenses/ for a full explanation
% of the Creative Commons licenses.

% DOCUMENT CLASS AND CT.STY
% All CT papers start with these two lines. Do not change make
% any changes in the ct.sty file as we use our own copy.
\documentclass[12pt]{article}
\usepackage{ct}

% GEOMETRY AND SPACES
% To keep the style homogeneous among all CT papers, please
%   * remove all commands that change parameters such as margins or page sizes. 
%   * avoid using any vspace, hspace, newpage, and other spacing commands.

% PACKAGES
% The following packages are already loaded in the style file:
%   * amssymb, amsthm, amsmath for mathematics,
%   * graphicx for images,
%   * hyperref and cleveref for references.
% Load your own packages below only if they are really needed:
% \usepackage{...}

% THEOREM ENVIRONMENTS
% The following environments are already declared in the style file:
%   * theorem-like environments: theorem, lemma, corollary, proposition, fact, observation, claim
%   * definition-like environments: definition, example, conjecture, open, problem, question
%   * remark-like environments: remark, note
% Declare your own environments below only if needed:
% \newtheorem{myenv}[theorem]{MyEnvironment}

% SPECIFICATIONS
% The editors will insert the specifications of your paper.
\specs{n}{vol (issue)}{year}{}

% DATES
% Give the submission and acceptance dates in the format shown.
% The editors will insert the publication date in the third argument.
\dateline{Jan 1, 2020}{Jan 2, 2020}{TBD}

% KEYWORDS
% Give one or more keywords separated by commas. No dot at the end.
\keywords{lattice polytopes, unimodular covers, integer decomposition property}

% SUBJECT CODES
% Give one or more subject codes separated by commas. No dot at the end.
% Codes are available from http://www.ams.org/mathscinet/freeTools.html
\MSC{52B10, 52B20, 52C17}

% TITLE
% If needed, include a line break (\\) at an appropriate place in the title.
\title{Unimodular covers of 3-dimensional\\ parallelepipeds and Cayley sums}

% AUTHORS AND AFFILIATIONS
% Input author, affiliation, address and support information as follows.
% The address should include the country, but does not have to include the street address. 
% Give at least one email address.
% Grants and institutional support information should be included in the thanks command. Other
% acknowledgements to colleagues or referees should appear in the Acknowledgements sections
% at the end of the paper, before the bibliography.

\author[1]{Giulia Codenotti\thanks{}}
\author[2]{Francisco Santos\thanks{Supported by grants PID2019-106188GB-I00 funded by MCIN/AEI/10.13039/501100011033 and CLaPPo (21.SI03.64658) of Universidad de Cantabria and Banco Santander}}
%\author[3]{Some Third Author}

% Write your affiation
\affil[1]{%
% Name of Department, Name of Institution, City and / or State, Country
Institute of Mathematics, Freie Universit\"at Berlin,

% leave a blank line and put your email here 
\email{giulia.codenotti@fu-berlin.de}%
}

% In case some authors share the same affiliation, use the following style.
% Do not use 'merging' of emails from the same institution such as \email{\{ssa,sta\}@uwn.edu.au}%
\affil[2]{%
% Name of Department, Name of Institution, City and / or State, Country
Department of Mathematics, Statistics and Computer Science, University of Cantabria, Spain

% leave a blank line and write the emails in the author's order
\email{francisco.santos@unican.es}%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% AUTHORS COMMANDS
% Enter here all commands you need (and no more) in this paper.
%\newcommand{\F}{ \ensuremath{\mathbb{F}}}
\newcommand{\N}{ \ensuremath{\mathbb{N}}}
\newcommand{\Z}{ \ensuremath{\mathbb{Z}}}
%\newcommand{\C}{ \ensuremath{\mathbb{C}}}
\newcommand{\R}{ \ensuremath{\mathbb{R}}}

\newcommand{\width}{\operatorname{width}}
\newcommand{\area}{\operatorname{area}}
\newcommand{\conv}{\ensuremath{\mathrm{conv}}\hspace{1pt}}
\newcommand{\cayley}{\operatorname{Cay}}

\newcommand{\vecline}[1]{\langle \vec #1 \rangle}

%\newcommand{\Image}{\ensuremath{\mathrm{Im}}\hspace{1pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%\writedatatofile

% ABSTRACT
% CT papers must include an abstract. The abstract should consist of a
% succinct statement of background followed by a listing of the
% principal new results that are to be found in the paper. The abstract
% should be informative, clear, and as complete as possible. Phrases
% like "we investigate..." or "we study..." should be kept to a minimum
% in favor of "we prove that..."  or "we show that...".  Do not
% include equation numbers, unexpanded citations (such as "[23]"), or
% any other references to things in the paper that are not defined in
% the abstract. The abstract may be distributed without the rest of the
% paper so it must be entirely self-contained.  Try to include all words
% and phrases that someone might search for when looking for your paper.
% You can use some basic LaTeX commands in the abstract, but not any
% user defined macros.

@@

% TABLE OF CONTENTS, LIST OF FIGURES, LIST OF TABLES
% Please, do not include a table of contents, a list of figures, or a
% list of tables. They will be removed by the editors (and the command
% is actually redefined in the ct.sty file).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ACKNOWLEDGEMENTS
% Include acknowledgements to colleagues and referee here.
% Funding and grant support should appear in footnotes on the front page, using the 
% thanks command in the authors command (see above).

\section*{Acknowledgements}
We  thank two anonymous referees for helpful comments on a previous version of this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% BIBLIOGRAPHY
% Pease provide us with a bibtex file for your bibliography
% You can find examples in ct-sample.bib. 
% Please use the correct entrytype 
%     article: any article published in a periodical like a journal article or magazine article
%     book: a book
%     booklet: like a book but without a designated publisher
%     conference: a conference paper
%     inbook: a section or chapter in a book
%     incollection: an article in a collection
%     inproceedings: a conference paper (same as the conference entry type)
%     manual: a technical manual
%     masterthesis: a Masters thesis
%     misc: used if nothing else fits
%     phdthesis: a PhD thesis
%     proceedings: the whole conference proceedings
%     techreport: a technical report, government report or white paper
%     unpublished: a work that has not yet been officially published
%
% When it exists, please add a DOI to your reference using the doi field, this will be shown as a link in the final pdf
% Similarly for preprints, please put the arXiv reference into the eprint field 
% When necessary, you can provide a link through the URL field. Please do not give both the URL and the DOI.
%
% We encourage you to use MathSciNet https://mathscinet.ams.org/mathscinet
% or other equivalent bibliography databases to get full and correct bibliographic entries.

\bibliographystyle{alphaurl}
\bibliography{unimodular-covers}
